Deciphering the Trends: A Comprehensive Analysis of US Birth Rates and Educational Attainment from 1980 to 2020

### 2024-02-06 outputs/paper/paper.qmd
Added SSRP

```{r}
knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
```
Code and data supporting this analysis are available at https://github.com/AlexanderG123/usa_birthrate

>>>>

```{r}
knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
```
Code and data underpinning this paper are available at: https://github.com/AlexanderG123/usa_birthrate. Selected aspects of the original paper that underpins this paper were reproduced and a record of this is available at: DOI : https://doi.org/10.48152/ssrp-g8j2-3h68
